<span class=font2><b>4()8&nbsp;</b><i>Notes and Observations, by </i><b>D</b><span class=font1><b>r. </b></span><b>Miller</b>. [September,</span>

<span class=font2><b>T</b><span class=font1><b>yphoid </b></span><b>F</b><span class=font1><b>ever.</b></span><span class=font0>---</span>A late German writer, Dr. F. C. Miller, says in
regard to the treatment of Typhoid Fever:</span>

<span class=font2>&quot; The general recommendation of starvation and depletion by the
French School will never lead us Germans to adopt their extreme notions
however high they are lauded. We shall never as practitioners of
medicine, become Red Republicans on the sufferings of humanity.</span>

<span class=font2>It is true with us there are some who pass encomiums on Calomel as an
abortive remedy in this form of fever, yet others who view the disease
and that agent from a <b>R</b><span class=font1><b>ational </b></span>point of view'know mercury at the
best is a deceitful agent, and sometimes proves very disadvantageous
and greatly destructive.</span>

<span class=font2>The typhoid process sometimes proceeds rapidly and with great
severity, but mainly through dietetical and therapeutical errors. The
obstruction of the bowels which is often present in the commencement
of the disease, may by the injudicious use of laxatives or cathartics
be changed to a severe or unmanageable diarrhoea. Many physicians
have, by ordering purgatives, made it necessary to also order a coffin.</span>

<span class=font2>The treatment for Typhoid Fever adopted by the physicians of
Vienna seldom embraces either Emetics, Cathartics, or Venesection.
They give an infusion of a few grains of Ipecacuanha in the congestive
or nervous stage, together with Chlorine water, and a little dilute
Aromatic Sulphuric Acid in the evening, and where there are severe
exascerbations, with any appearance of intermittance they give about
<i>four </i>grains of Sulph. Quinia daily. For the diarrhoea they prescribe
Alum. When the skin remains presistently hot, arid there is great
prostration, particularly if there is profuse diarrhoea they give camphor
and alum by the mouth and in injections.</span>

<span class=font2>If the disquiet and restlessness continues, but is more marked dur-
ing the night, and especially if there be a bloody diarrhoea, they give
Musk and Camphor in injections. They also apply as indicated, cold
water to the head and cold washings to the whole body, made of equal
parts of water and vinegar, so long as the skin remains hot and dry.
For the purpose of hastening convalescence they lay great stress upon
tepid bathing. This course I consider progressive and Rational treat-
ment.&quot;</span>

<span class=font2><b>P</b><span class=font1><b>hlegmasia </b></span><b>D</b><span class=font1><b>olens.</b></span><span class=font0>---</span>This disease is known by the names of White
Leg, Swelled Leg, Milk Leg, White Swelling of Lying-in Women,
Phlegmasia dolens alba. <i>Obstructus venerarum puerperalis.</i></span>

<span class=font2>We find this a disease of lying-in women, and it commences sooner
or later with febrile excitement, and a painful, bright white, strained,</span>\endinput
