<span class=font1><b>1857.1</b></span>

<span class=font1><i>Abortion---The Medical Observer.</i></span>

<span class=font1><b>411</b></span>

<span class=font1>of this city lias extended I consider the charge a base slander, but as I
am not on intimate terms with the members of that Faculty I cannot
answer for them and I leave them to endure the odium the charge has
cast upon them or prove its falsity as they see fit.&quot;</span>

<span class=font1>Being unwilling to allow such a charge as that contained in the
<i>Observer </i>to rest upon the profession, I expressed my full conviction
that it was a &quot;base slander,&quot; leaving those more particularly interested
to answer for themselves, for while I would ever do all I can to sus-
tain the reputation of the profession, I would not presume to be bet-
ter acquainted with the character and practice of Dr. Bauer's friends
than he is.</span>

<span class=font1>But hardly had the ink become dry on the pages of the <b>J</b><span class=font0><b>ournal</b></span>, ere
I received the following <i>public document, </i>made intentionally public by
being sent in the form of an <i>open circular </i>through the City Post-Office.</span>

<span class=font1><i>&quot; Office of the Cin. Med. Observer.</i></span>

<span class=font1><b>A</b><span class=font0><b>ugust </b></span><b>15, 1857.</b></span>

<span class=font1>Dr. <b>C</b><span class=font0><b>leaveland.---</b></span><i>Sir.</i>---As you are fully aware---the allusion to
Dr. Bauer, in your article on <i>&quot;Abortion&quot; </i>in the Aug. No. of the
<b>C</b><span class=font0><b>ollege </b></span><b>J</b><span class=font0><b>ournal </b></span>is grossly and inexcusably false; and the personal
reference to his friends here are as intensely malicious---as unwarrant-
ed ;---the <i>&quot;Observer&quot; </i>therefore declines further exchange.</span>

<span class=font1><b>E</b><span class=font0><b>dward </b></span>B. <b>S</b><span class=font0><b>tevens.&quot;</b></span></span>

<span class=font1>During the present, &quot;heated term&quot; many have found it difficult to
keep up an equipoise of temperature, but I am of the opinion that the
publisher of the <i>&quot;Observer&quot; </i>must now have as much internal as
external caloric, and according to the Thomsonian notion he is on
the high road to health and happiness. In regard to the &quot; No. 6 &quot; the
&quot;Composition,&quot; and the &quot;Capsicum &quot; which he has introduced into
his prescription, since he has manifested a great familiarity with them
I shall leave the readers of the <b>J</b><span class=font0><b>ournal </b></span>to decide if the terms <i>'&quot;false&quot;
</i>and &quot; <i>malicious&quot; </i>do not rather belong to those who publish the &quot; <i>Ob-
server </i>,&quot; and write letters, and not to myself.</span>

<span class=font1>I have stated no falsehood, but cannot tell whether Dr. Bauer has
or not. I have made no &quot;malicious&quot; accusation against the Editors of
the <i>Observer, </i>or the former Faculty of the Miami Medical College. ♦
Neither have I allowed the use of the <b>J</b><span class=font0><b>ournal </b></span>of which I am pub-
lisher or any other to do the same. Both the <b>C</b><span class=font0><b>ollege </b></span><b>J</b><span class=font0><b>ournal </b></span>and
its publisher have ever done what they could to sustain the char-
acter and the reputation of the profession, and both can possibly survive
the terrible catastrophy of the threatened loss of &quot; exchange&quot; with the</span>\endinput
