<span class=font2><i>Queries Answered. </i>[September,</span>

<span class=font2>QUERIES ANSWERED.
<span class=font1><b>&quot;catarrh.&quot;</b></span></span>

<span class=font2>I <span class=font1><b>will </b></span>make the following query to which I would be pleased to get
an answer in the next No. of the <b>C</b><span class=font1><b>ollege </b></span><b>J</b><span class=font1><b>ournal</b></span>. I am annoyed con-
siderably with noises in my ears, it being however almost entirely confined
to the left one. Sometimes the noise is of a ringing'character; at others
there is a roaring and rushing. It is almost constant, yet frequently
more marked in the evening and aggravated by every slight cold I take.
I have no pain in the ears but sometimes a slight itching ; I have been
very subject to irritation of the larynx from the slightest check of perspi-
ration. My tonsils also were formerly irritated and somewhat en-
larged, but by means of astringents and stimulants locally applied they
were reduced and have not given me any trouble for some months. My
general health is good, but I have been somewhat troubled with papular
eruptions on the face. I have at times felt more or less dizziness when
raising my head suddenly after having bowed down ; and not long since,
after having taken a slight cold, the noise was greatly augmented in my
ear and I became quite dizzy and for a short time (after a somewhat full
meal), was unable to walk straight. My hearing has-been slightly affected.
Now what is most probably the difficulty and what course of treatment
would you recommend % I might have mentioned that I never had acute
inflammation of the ear either external or internal, nor have I been sub-
ject to headache.</span>

<span class=font2><b>A</b><span class=font1><b>nswer.</b></span><span class=font0>—</span>Your annoyances probably arise from chronic inflammation
of the mucous membrane of the nares and pharynx ; the &quot;ringing&quot; in the
ears is produced by a partial obstruction of the Eustachian tube, preven-
) ting a free passage of air from the throat to the ear. The laryngeal diffi-
culty depends upon the same disease which is continued into the vocal
organ ; and the dizziness is consequent upon a congested state of the ves-
sels of the head, the blood being determined thither in undue quantities
by the irritation existing'in and about the pharynx. The disease, in the
acute form called &quot; coryza&quot; and &quot; influenza&quot; is a common one, especially
in countries subject to great atmospheric vicissitudes.</span>

<span class=font2>The lower animals are subject to a similar disease. It is well known
that within the heads cf mammalia there are extensive pneumatic cavi-
ties communicating with the mouth and nose. These cavities in man
are called, &quot;antrums,&quot; as that of Ilighmore ; and &quot;sinuses,&quot; as the fron-
tal, ethmoidal and sphenoidal sinuses. The elephant and the owl derive
considerable reputation for intellectual profundity from the prominence
given by these airy cells.   Pneumatic cavities in the bones of birds</span>
