<span class=font1><b>430 <sub>;</sub>&nbsp;.&nbsp;</b><i>Book Notices. </i>[September,</span>

<span class=font1>&quot; We loathe to be classed among the fossil remains of by-gone ages,
as belonging to that order of men who, if they had been born during
an eclipse of the sun would have protested against the return of its
light, or, if they had been born in the ark during the deluge of Noah
would have remonstrated against the subsidence of the waters.&quot;</span>

<span class=font0><b><i>The American Eclectic Practice of Medicine. </i>Bv I. G. Jones, M. D., late Professor of the
Theory and Practice of Medicine in &quot; The Eclectic Medical Institute of Cincinnati,&quot;
etc., etc. Extended and Revised at request of the Author by Wm. Sherwood, M. D.,
Professor of Medical Practice and Pathology in &quot; The Eclectic College of Medicine;&quot;
formerly Professor of General, Special and Pathological Anatomy in &quot;The Eclectic
Medical Institute of Cincinnati/' etc. In two volumes. Cincinnati: Moore, Wil-
stach, Keys and Co., 25 West Fourth Street. 1857.</b></span>

<span class=font1><b>W</b><span class=font0><b>e </b></span>are not informed how much extension and revision these volumes
will undergo by Prof. Sherwood, but his connection with the work when
first issued and his well known talent as a writer and a speaker must
entirely satisfy our readers that the forthcoming books will be every
way worthy those who are engaged in their production.</span>

<span class=font0><b><i>The American Journal of Insanity </i>for July.</b></span>

<span class=font1><b>I</b><span class=font0><b>f </b></span>physicians will admit as true the statement of <b>G</b><span class=font0><b>rotius </b></span>that &quot; The
care of the human mind is the most noble branch of Medicine,&quot; they
will appreciate the value of this admirable Quarterly which is entirely
devoted to that speciality. This number is the initial one to the four-
teenth volume, and we think fully equal to any of its predecessors.</span>

<span class=font0><b><i>The Half-Yearly Abstract of the Medical Sciences, </i>etc. etc., edited by W. H. Ranking, M. D.
and C. B. Radoliffe, M. <i>D., </i>No. 25, January to July, 1857. Reprinted by Lindset and
Blakiston, Philadelphia.</b></span>

<span class=font1><b>W</b><span class=font0><b>e </b></span>have already expressed the opinion that this is the <i>best </i>Medical
Periodical published for the active practitioner, and that no one who
has become acquainted with its value can afford to do without it.</span>

<span class=font0><b><i>Alphabetical Index to Braithwaite's Retrospect; </i>Embracing Part I.—XXXIV. 1840—1857
and comprising the whole seventeen years of Republication. New York, Stringer and
Townsend. 1857.</b></span>

<span class=font1><b>T</b><span class=font0><b>his </b></span>is an admirable and most valuable index to the well-known
Semi-Yearly publication of Dr. <b>B</b><span class=font0><b>raithwaite</b></span>, and the many readers of
that excellent work will welcome it with great pleasure.</span>

<span class=font0><b><i>The British and Foreign Medico-Chirurgical Review; </i>or Quarterly Journal of Practical
Medicine and Surgery.   July, 1857.</b></span>

<span class=font1><b>T</b><span class=font0><b>he </b></span>reprint of this work, by the Messrs. <b>W</b><span class=font0><b>ood</b></span>, always comes
promptly. The present number fully sustains the high reputation it
has acquired during a period of near forty years continuous publication.</span>\endinput
