<span class=font1>432</span>

<span class=font1><i>Miscellany.</i></span>

<span class=font1>[September,</span>

<span class=font0><b>M S CELL ANY.</b></span>

<span class=font0><b>THE BOSTON JOURNAL AND PATENTS.</b></span>

<span class=font1><b>I</b><span class=font0><b>t </b></span>is somewhat amusing to see the various <i>inconsistencies </i>would-be
conservatives often indulge in. Even the fossiliferous <i>Boston Medical
and Surgical Journal, </i>the type of conservatism has recently com-
mended a patented article, and according to the Ethics of the Am.
Med. Association, has now placed itself quite beyond the pale of the
<i>regular </i>profession. In an Editorial published in the Journal for June
the 25th, it adopts the usual style of the paid Editorials of the secular
papers while puffing nostrums, and says:</span>

<span class=font1>&quot; Although we are always reluctant to recommend any medicine or
instrument, with the virtues of which we are not personally acquainted,
we are induced by the favorable opinion expressed to us by two of
the most eminent physicians of this city concerning <i>Parker's Patent&quot;
</i>etc., etc., <sup>u</sup> to invite the attention of the profession to a contrivance
which seems admirably adapted,&quot; etc., etc. In February last while
giving a commendatory notice of another patented article, the Boston
Journal was a little more cautious, and left out the word &quot;patent,&quot;
possibly with the idea of thus escaping the fiat of excommunication
which was pronounced against the State Medical Society, of Ohio.</span>

<span class=font0><b>&quot; Who shall guard the Shepherds ?&quot;</b></span>

<span class=font0><b>NEURALGIA.</b></span>

<span class=font1>A <span class=font0><b>correspondent </b></span>who has read Dr. <b>B</b><span class=font0><b>arrows</b></span>' article published on
page 256 of the <b>J</b><span class=font0><b>ournal</b></span>, has referred to a work by Dr. <b>M</b><span class=font0><b>egelin </b></span>entitled
<i>&quot;Researches in regard to Facial Neuralgia&quot; </i>and published at Stras-
bourg in 1816. We will consider it a favor to be furnished with still
farther information in regard to this book, and the remedies used by Dr.
<b>M</b><span class=font0><b>egelin.</b></span></span>

<span class=font0><b>MEETING OF THE INDIANA ECLETIC STATE MEDICAL ASSOCIATION.</b></span>

<span class=font1><b>T</b><span class=font0><b>he </b></span>members of the Indiana Eclectic Medical Association, and all
Eclectic physicians throughout the State, are requested to meet at the
city of Indianapolis on the 6th day of Oct., 1857, at 2 o'clock <b>F. M.,
</b>for the purpose of perfecting an organization of the faculty throughout
the State. A general attendance is earnestly solicited as business of im-
portance to the profession will come before the meeting.   By order,</span>

<span class=font1>O. H. <b>K</b><span class=font0><b>endrick, </b></span><i>Secretary.</i></span>

<span class=font0><b>MARRIED.</b></span>

<span class=font0><b>At North Brookfield, Mass , 4th inst., Henby T. Bates, M. D., of Lowell Mass., to Miss
Lottie H. Bush, of North Brookfield.</b></span>\endinput
