\oldpage{408}

\textsc{Typhoid Fever}.---A late German writer, Dr.\ F.~C.\ Miller, says in
regard to the treatment of Typhoid Fever:

``The general recommendation of starvation and depletion by the
French School will never lead us Germans to adopt their extreme notions
however high they are lauded. We shall never as practitioners of
medicine, become Red Republicans on the sufferings of humanity.

It is true with us there are some who pass encomiums on Calomel as an
abortive remedy in this form of fever, yet others who view the disease
and that agent from a \textsc{Rational} point of view know mercury at the
best is a deceitful agent, and sometimes proves very disadvantageous 
and greatly destructive. \typo{should be leader}{* * * *}

The typhoid process sometimes proceeds rapidly and with great
severity, but mainly through dietetical and therapeutical errors. The
obstruction of the bowels which is often present in the commencement
of the disease, may by the injudicious use of laxatives or cathartics
be changed to a severe or unmanageable diarrhœa. Many physicians
have, by ordering purgatives, made it necessary to also order a coffin.

The treatment for Typhoid Fever adopted by the physicians of
Vienna seldom embraces either Emetics, Cathartics, or Venesection.
They give an infusion of a few grains of Ipecacuanha in the congestive
or nervous stage, together with Chlorine water, and a little dilute
Aromatic Sulphuric Acid in the evening, and where there are severe
exascerbations, with any appearance of intermittance they give about
\emph{four} grains of Sulph. Quinia daily. For the diarrhœa they prescribe
Alum. When the skin remains \typo{persistently}{presistently} hot, arid there is great
prostration, particularly if there is profuse diarrhœa they give camphor
and alum by the mouth and in injections.

If the disquiet and restlessness continues, but is more marked during
the night, and especially if there be a bloody diarrhœa, they give
Musk and Camphor in injections. They also apply as indicated, cold
water to the head and cold washings to the whole body, made of equal
parts of water and vinegar, so long as the skin remains hot and dry.
For the purpose of hastening convalescence they lay great stress upon
tepid bathing. This course I consider progressive and Rational treatment.''

\textsc{Phlegmasia Dolens}.---This disease is known by the names of White
Leg, Swelled Leg, Milk Leg, White Swelling of Lying-in Women,
Phlegmasia dolens alba. \foreign{Obstructus venerarum puerperalis}.

We find this a disease of lying-in women, and it commences sooner
or later with febrile excitement, and a painful, bright white, strained,\endinput
