\oldpage{419}
\chapter*{Editorial Department}

\fancybreak{*}

\section*{State Medical Associations.}

\SectionStartWords{That} a State Medical Association, based upon correct principles and
sustained and conducted with the proper spirit, would be of great benefit
to the profession and to the community we have no doubt. Such an
institution would do much in developing the resources of the healing
art, correcting errors in medical practice and establishing a high standard
of qualifications as a criterion of professional respectability. We
are cons trained however, to say that such results from Associations that
have heretofore been organized we have not seen. In the old school
organization no rule has ever been adopted that has had the practical
effect of excluding ignorant and unworthy members who have tact
enough to maintain the claim of regularity (\foreign{i.~e.}), subserviency to the
party dictum in regard to medical faith; though their rules are potent
in ostracising any one, however learned and accomplished, who has boldness
to think for himself and to express his thoughts.

As some of our friends in different States are making the attempt to
form State Eclectic Medical Associations we deem it an opportune
season to speak a word of fraternal admonition on this subject. We
have no right---we have no desire---to dictate, yet since this is a matter
in which all are directly or indirectly interested and since we have been
repeatedly addressed on the subject, it will not, we hope, be deemed
arrogant in us to suggest, that an Eclectic Association formed at the
present time should take a position far above that occupied by those
to which we have referred. It should take a position that shall save
it from the odium of fostering and indorsing ignorance and charlatanry,
under the cloak of professional dignity, and which shall secure to true
merit a full opportunity of being appreciated and sustained. In short
an Eclectic Association should, if practicable, be composed of members
only who have thoroughly qualified themselves for their profession, and
whose object is, not to gain notoriety nor manufacture reputation for
themselves, but to mutually improve each other, and promote the common
interests of all: of men who are willing and able to contribute by
their labors to the advancement of science, instead of making the
association bend under the weight of their self-vaunting ambition or
blush at the demonstrations of their ignorance.

But here arises a question which must be met at the outset and
upon the judicious settlement of which greatly depends the reputation,
harmony and usefulness of the association. Who shall constitute the
body?  Shall any one \emph{claiming} to be a physician be admitted as a\endinput
