\oldpage{420}member, irrespective of professional attainments? The vast number
of ignoramuses who are to be found throughout the land professing to
be ``doctors,'' might furnish such an association with a formidable roll
so far as numbers are concerned, but we can readily conceive of such
an organization, with which no man who had any self-respect or any professional
reputation to lose would willingly be identified. But by what
means shall the ignorant and unprincipled be excluded? We fear it
will be difficult to do it successfully by any rule. Shall a diploma be
a sure passport to membership? Many men hold diplomas who have
very little claim besides to professional character, and who by obtaining
such documents knowing their own incompetency, have proven themselves
to be unworthy of confidence.

It seems however that there is no practicable criterion of membership
that is so nearly equitable as one having reference to graduation.
A diploma from a legally authorized Medical College with the usual
number of chairs filled by reputable professors, and requiring the usual
amount of study and collegiate instruction as a prerequisite to graduation
\emph{should} be prima facie evidence of respectable professional attainments;
and although there are diplomas which have been issued by
institutions claiming to be respectable, in the hands of men every way
unworthy, the admission of such would certainly be a less evil than to
admit in addition to these the legions of pretenders who have neither
diplomas nor medical education. We know that such a rule would exclude
some who are far above mediocrity as successful and scientific
practitioners, but such could soon obtain diplomas, and if they are men
of professional spirit they would be willing to suffer temporary inconvenience
for the sake of excluding the unworthy.

If we had the drafting of a constitution we should probably incorporate
at least four rules bearing on membership, embodying the following
principles:

1.\quad{}A voting member must be a graduate of a legally constituted
Medical College that requires the usual \typo{curriculum}{curiculum} of study before graduation.

2.\quad{}Whenever it should appear that a member had obtained his
diploma without complying with legal requirements he should be expelled.

3.\quad{}No one who professed to possess knowledge which he would not
impart to the profession, or who practiced with or encouraged the sale of
secret nostrums, should retain his membership.

4.\quad{}Reputable non-graduates should be eligible by vote of the association
to the position of honorary membership, with the privilege of
participating in the deliberations.\endinput
